# DAILY PERFORMANCE REPORT FOR...

```{r echo=FALSE}
start <- as.Date(Sys.time() - (60*60*24))
start
```


```{r echo=FALSE, message=FALSE,warning=FALSE}
#gtc <- rbind(gtc, gtc1)

library(stringr)
library(dplyr)
library(ggplot2)
library(xlsx)
library(rJava)
setwd('C:/Programs/gtc_tasks/performance_task_daily/')



```


```{r echo=FALSE, message=FALSE,warning=FALSE}
filename <- paste(start, "_", "results.xlsx", sep = '')
filename <- paste("spreadsheets/",filename,sep="")
# load package for sql
library(DBI)
library(RODBC)
# connect to database
odbcChannel <- odbcConnect('Rstudio', uid='Daria Alekseeva', pwd='Welcome30')

# query for last day which is not in archive yet
gtc  <- sqlQuery( odbcChannel, 
"
declare @FROM datetime
declare @TO datetime
set @FROM = DATEADD(DAY, -1, CONVERT(CHAR(10), getdate(), 111))
set @TO = DATEADD(DAY, -1, CONVERT(CHAR(10), getdate(), 111)) +'23:59:59'
select j.id, ca.number as 'AccountNumber', ca.name as 'AccountName', cg.name as 'Grade', j.jobDate, jh.actionDate as 'ArrivalTime',
DATEDIFF(minute, j.jobDate, jh.actionDate) as 'MinDiff',
c.name as 'Driver',
isnull(vt.name, 'Partners') as 'VehicleType',
adr.name as 'PickUpPC',
j.asap,
j.jobStatus,
case when j.creationType=0  then 'Echo'
	 when j.creationType=1  then 'Web'
     when j.creationType=2  then 'IOS'
	 when j.creationType=3  then 'Android'
     when j.creationType=4  then 'Oscar'
   	 when j.creationType=5 then 'One Transport'
     when j.creationType=7  then 'Persona'
	 when j.creationType=9  then 'GTC overflow iOS'
   	 when j.creationType=10  then 'GTC overflow Android'
   	 when j.creationType=11  then 'iOS Lite'
   	 when j.creationType=12  then 'Android Lite'
	 when j.creationType=14  then 'iOS GTC'
	 when j.creationType=15  then 'Android GTC'
	 when j.creationType=16 then 'Cityfleet'  end 'creationType',
(select top 1 jh.shortArg from echo_core_prod.dbo.job_history jh where jh.jobReference=j.id and jh.shortArg like '%about Late to Pickup') as 'NotificationLate',
(select top 1 username from echo_core_prod..job_history where actionType=18 and jobReference=j.id) as 'AllocatedBy',
DATEPART(hh, jobdate)*60 + DATEPART(mi, jobdate) 'TimeInMin'
from echo_core_prod.dbo.jobs j
LEFT JOIN (select jh.jobReference, min(jh.actionDate) as 'actionDate'from echo_core_prod.dbo.job_history jh 
 where jh.shortArg = 'Arrived' and jh.actionType = 1 group by jh.jobReference) jh
 ON jh.jobReference = j.id 
LEFT JOIN Echo_core_prod.dbo.customer_accounts ca
 on ca.id = j.customer_account_id
LEFT JOIN Echo_core_prod.dbo.customer_grades cg
 on cg.id=ca.grade_id
LEFT JOIN Echo_core_prod.dbo.callsigns c
 on c.driver_id=j.driver_id
LEFT JOIN
 (select adr.name, st.job_id
 from Echo_core_prod.dbo.job_stops st
 inner join
 (select a.fullStr, p.name, a.id from Echo_core_prod.dbo.addresses a inner join Echo_core_prod.dbo.areas p on a.postcode_id = p.id) adr
 on adr.id = st.address_id where st.orderNumber = 0) adr
 on j.id = adr.job_id
Left Join Echo_core_prod..vehicles v on j.vehicle_id=v.id Left join Echo_core_prod..models m on v.model_id=m.id Left join Echo_core_prod..vehicle_types vt on m.vehicle_type_id=vt.id
where j.jobstatus in (7,10) 
and j.creationtype not in (9,10,11,12)
and j.jobDate between @FROM and @TO

order by j.id


")


##query for each 5 min driver status 
drivers <- sqlQuery( odbcChannel, 
"
declare @FROM datetime
declare @TO datetime
set @FROM = DATEADD(DAY, -1, CONVERT(CHAR(10), getdate(), 111))
set @TO = DATEADD(DAY, -1, CONVERT(CHAR(10), getdate(), 111)) +'23:59:59'

select * 
from Archive_echo_core_prod.dbo.OnlineDriversHistory 
where timestamp between @FROM and @TO ")


jobhistory <- sqlQuery( odbcChannel, 
"
declare @FROM datetime
declare @TO datetime
set @FROM = DATEADD(DAY, -2, CONVERT(CHAR(10), getdate(), 111))
set @TO = DATEADD(DAY, -1, CONVERT(CHAR(10), getdate(), 111)) +'23:59:59'

select j.id, j.jobDate, ca.number, ca.name, c.name 'UserName' ,
(select min(jh.actionDate) from
(select * from Echo_core_prod..job_history union select * from Archive_echo_core_prod..job_history) jh 
where j.id = jh.jobReference and jh.shortArg = 'Accepted') 'TimeAccepted',
(select min(jh.actionDate) from
(select * from Echo_core_prod..job_history union select * from Archive_echo_core_prod..job_history) jh 
where j.id = jh.jobReference and jh.shortArg = 'Arrived') 'TimeArrived',
(select min(jh.actionDate) from
(select * from Echo_core_prod..job_history union select * from Archive_echo_core_prod..job_history) jh 
where j.id = jh.jobReference and jh.shortArg = 'POB') 'TimePoB',
(select min(jh.actionDate) from
(select * from Echo_core_prod..job_history union select * from Archive_echo_core_prod..job_history) jh 
where j.id = jh.jobReference and jh.shortArg = 'Completed') 'TimeCompleted'
from echo_core_prod..jobs j
left join echo_core_prod..customer_accounts ca on j.customer_account_id = ca.id
left join Echo_core_prod..callsigns c on c.driver_id=j.driver_id
where j.jobStatus = 7 and j.jobDate between @FROM and @TO and c.name is not null
and c.name not like 'DD%'
")


cashblock <- sqlQuery( odbcChannel, 
"
declare @FROM datetime
declare @TO datetime
set @FROM = DATEADD(DAY, -6, CONVERT(CHAR(10), getdate(), 111))
set @TO = DATEADD(DAY, -1, CONVERT(CHAR(10), getdate(), 111)) +'23:59:59'

	select daa.id, daa.REVTYPE, daa.fromTime, daa.toTime, r.timestamp, r.username,
	case daa.dayOfWeek when 1 then 'Monday'
					   when 2 then 'Tuesday'
					   when 3 then 'Wednesday'
					   when 4 then 'Thursday'
					   when 5 then 'Friday'
					   when 6 then 'Saturday'
					   when 0 then 'Sunday' end 'Weekday'
	from echo_core_prod..day_availabilities_AUD daa
	join echo_core_prod..REVINFO r on r.id=daa.REV
	where timestamp between @FROM and @TO
	and type = 1
	and customer_account_id = 3743
")




odbcClose(odbcChannel)



```

## G10 Block yesterday


```{r echo= FALSE,fig.width=18, fig.height=10,warning=FALSE, message= FALSE}

yesterday <- weekdays(Sys.time() - (24*60*60))
#uncomment to run for yesterday
cashblock <- cashblock[cashblock$Weekday == yesterday,]


#cashblock <- cashblock[cashblock$Weekday == 'Friday',]
cashblock <- cashblock[!(cashblock$fromTime == 0 & cashblock$toTime == 2359),]


if (nrow(cashblock) > 0) {
cb_from_to <- data.frame(id=unique(cashblock$id))
cb_from_to$from <- 0
cb_from_to$to <- 0

    for (each in cb_from_to$id){
  cb_from_to[cb_from_to$id == each,]$from <- cashblock[cashblock$id == each,][1,]$fromTime
  cb_from_to[cb_from_to$id == each,]$to <- cashblock[cashblock$id == each,][nrow(cashblock[cashblock$id == each,]),]$toTime
  }
# add '0' before 3 digit numeric time value
cb_from_to$from <- sapply(cb_from_to$from, function(x) str_pad(x,width=4,pad=0))
cb_from_to$to <- sapply(cb_from_to$to, function(x) str_pad(x,width=4,pad=0))


# convert time into 00:00 format
cb_from_to$from<-lapply(cb_from_to$from, function(x) strftime(as.POSIXct(x, format = "%H%M"), format="%H:%M"))
cb_from_to$to <-lapply(cb_from_to$to, function(x) strftime(as.POSIXct(x, format = "%H%M"), format="%H:%M"))


# add date of block to each time and convert into time format
cb_from_to$from <- paste(as.Date(Sys.time() - (24*60*60)), cb_from_to$from)
cb_from_to$to <- paste(as.Date(Sys.time() - (24*60*60)), cb_from_to$to)
cb_from_to$from <-strptime(cb_from_to$from, "%Y-%m-%d %H:%M")
cb_from_to$to <-strptime(cb_from_to$to, "%Y-%m-%d %H:%M")

# calculate pure time for each block
cb_from_to$BlockTime <- as.numeric(difftime(cb_from_to$to,cb_from_to$from, units =  'mins'))


df<-data.frame()

for (i in 1:(length(cb_from_to$BlockTime))) {
  if (cb_from_to[i,]$BlockTime > 60 & cb_from_to[i,]$BlockTime <=120) {
    a<-data.frame()
    a<- rbind(a,cb_from_to[i,])  
    a<- rbind(a,cb_from_to[i,]) 
    a[2,]$from<-a[2,]$from + 3600
    df<-rbind(df,a)
  } else if (cb_from_to[i,]$BlockTime > 120 & cb_from_to[i,]$BlockTime <=180) {
    a<-data.frame()
    a<- rbind(a,cb_from_to[i,])  
    a<- rbind(a,cb_from_to[i,])
    a<- rbind(a,cb_from_to[i,]) 
    a[2,]$from<-a[2,]$from + 3600
    a[3,]$from<-a[3,]$from + 7200
  } else if (cb_from_to[i,]$BlockTime > 180 & cb_from_to[i,]$BlockTime <=240) {
    a<-data.frame()
    a<- rbind(a,cb_from_to[i,])  
    a<- rbind(a,cb_from_to[i,])
    a<- rbind(a,cb_from_to[i,]) 
    a<- rbind(a,cb_from_to[i,]) 
    a[2,]$from<-a[2,]$from + 3600
    a[3,]$from<-a[3,]$from + 7200
    a[4,]$from<-a[4,]$from + 10800    
    df<-rbind(df,a)
  } else if (cb_from_to[i,]$BlockTime > 240 & cb_from_to[i,]$BlockTime <=300) {
    a<-data.frame()
    a<- rbind(a,cb_from_to[i,])  
    a<- rbind(a,cb_from_to[i,])
    a<- rbind(a,cb_from_to[i,]) 
    a<- rbind(a,cb_from_to[i,]) 
    a<- rbind(a,cb_from_to[i,])
    a[2,]$from<-a[2,]$from + 3600
    a[3,]$from<-a[3,]$from + 7200
    a[4,]$from<-a[4,]$from + 10800
    a[5,]$from<-a[5,]$from + 14400 
    df<-rbind(df,a)
  } else if (cb_from_to[i,]$BlockTime > 30 & cb_from_to[i,]$BlockTime <=60) {
    df<-rbind(df,cb_from_to[i,])
  } else if (cb_from_to[i,]$BlockTime > 300 & cb_from_to[i,]$BlockTime <=360) {
    a<-data.frame()
    a<- rbind(a,cb_from_to[i,])  
    a<- rbind(a,cb_from_to[i,])
    a<- rbind(a,cb_from_to[i,]) 
    a<- rbind(a,cb_from_to[i,]) 
    a<- rbind(a,cb_from_to[i,])
    a<- rbind(a,cb_from_to[i,])
    a[2,]$from<-a[2,]$from + 3600
    a[3,]$from<-a[3,]$from + 7200
    a[4,]$from<-a[4,]$from + 10800
    a[5,]$from<-a[5,]$from + 14400 
    a[6,]$from<-a[6,]$from + 18000
    df<-rbind(df,a)
  } else if (cb_from_to[i,]$BlockTime > 360 & cb_from_to[i,]$BlockTime <=420) {
    a<-data.frame()
    a<- rbind(a,cb_from_to[i,])  
    a<- rbind(a,cb_from_to[i,])
    a<- rbind(a,cb_from_to[i,]) 
    a<- rbind(a,cb_from_to[i,]) 
    a<- rbind(a,cb_from_to[i,])
    a<- rbind(a,cb_from_to[i,])
    a<- rbind(a,cb_from_to[i,])
    a[2,]$from<-a[2,]$from + 3600
    a[3,]$from<-a[3,]$from + 7200
    a[4,]$from<-a[4,]$from + 10800
    a[5,]$from<-a[5,]$from + 14400 
    a[6,]$from<-a[6,]$from + 18000
    a[7,]$from<-a[7,]$from + 21600
    df<-rbind(df,a)
    } else {
     df<-rbind(df,cb_from_to[i,]) }
}
df$BlockHour <-as.numeric(format( as.POSIXct(df$from), "%H"))
    df$Block <- 1
    df2<-data.frame(BlockHour =seq(0,23,1))
    
    x <- merge(df2,df,by='BlockHour', all = T)
    x[is.na(x$Block),]$Block <- 0
    x <- unique(x[c('BlockHour','Block')])
    block<-x[x$Block==1,]
    block
  
} else {
  print('No G10 block yesterday')
}
```


```{r echo=FALSE, message=FALSE,warning=FALSE}
match <- c('2200', '6443', 'G1', 'G2', 'G3', 'G4', 'G5', 'G6', 'G7', 'G8', 'G9.1', 'G9.5', 'GTC888', 'G50', 'G51', 'G5555', '7002', 'LONGTC1387')

gtc <- gtc[!(gtc$AccountNumber %in% match),]


###GTC
gtc$Hour <- format( as.POSIXct(gtc$jobDate), "%H")
gtc$Date <- format( as.POSIXct(gtc$jobDate), "%Y-%m-%d")
gtc$Weekday <- weekdays(as.POSIXct(gtc$jobDate)) 
gtc$MinDiff <- as.numeric(gtc$MinDiff)
gtc$Count <- 1

gtc$Type <- 'Account'

gtc[gtc$AccountNumber == 'G10' | gtc$AccountNumber == 'LHR',]$Type <- 'G10'

gtc[gtc$asap==1,]$asap <- 'asap'
gtc[gtc$asap==0,]$asap <- 'prebook'


# add column for 4 types of jobs
gtc$Type2 <- 'type'
gtc[gtc$asap == 'asap' & gtc$Type == 'G10',]$Type2 <- 'asap_g10'
gtc[gtc$asap == 'asap' & gtc$Type == 'Account',]$Type2 <- 'asap_account'
gtc[gtc$asap == 'prebook' & gtc$Type == 'G10',]$Type2 <- 'prebook_g10'
gtc[gtc$asap == 'prebook' & gtc$Type == 'Account',]$Type2 <- 'prebook_account'
## Performance

# save all jobs not cleaned for performance purpose
gtc2 <- gtc
```



```{r day and night shifts performance, echo=FALSE, message=FALSE,warning=FALSE}
#Day defined as 6:30 to 18:29 
#Night defined as 00:00 to 06:29 and 18:30 to 23:59
gtc$shift <- 'NightShift'
gtc[gtc$TimeInMin >= 390 & gtc$TimeInMin <= 1109,]$shift <- 'DayShift'
```


```{r echo=FALSE, message=FALSE,warning=FALSE}
### Day shift (6:30 to 18:29). Job Volume  
dayshift <- gtc[gtc$shift == 'DayShift',]
ds<-nrow(dayshift)
```


```{r echo=FALSE, message=FALSE,warning=FALSE}
### Night shift (00:00 to 06:29 and 18:30 to 23:59). Job Volume  
nightshift <- gtc[gtc$shift == 'NightShift',]
ns<-nrow(nightshift)
```


```{r echo=FALSE, message=FALSE,warning=FALSE}

# extract first part of postcode
library(reshape2)
library(stringr)
gtc_pc<- colsplit(string=gtc$PickUpPC, pattern=" ", names=c("GTCPart1", "GTCPart2"))

gtc_pc$PC <- 'PC'

pc <- c()

for (each in gtc_pc$GTCPart1){
  if (is.na(as.numeric(str_sub(each,-1,-1))))
  {
    x <- substr(each, 1, nchar(each)-1)
    pc <- c(pc, x)
   #print(x)
  } else
    pc <- c(pc, each)
    #print(each)
}

gtc_pc$PC <- pc




gtc$PC <- gtc_pc$PC





# exclude airports
match <- c('TW6', 'RH6', 'CM24', 'E16', 'LU2')
gtc <- gtc[!(gtc$PC %in% match),]

# exclude one transport
gtc <- gtc[(gtc$creationType != 5),]

# exclude morgan stanley
gtc <- gtc[(gtc$AccountNumber!='C6000'),]

gtc <- gtc[!is.na(gtc$MinDiff),]
```



```{r echo= FALSE,fig.width=18, fig.height=10,warning=FALSE, message= FALSE}
### Yesterday jobs on time in %%  

#### MORE DETAILED ARRIVALS
gtc$arrival_bucket <- '0'

gtc[gtc$MinDiff > 20 ,]$arrival_bucket <- '20+ min late'

gtc[gtc$MinDiff > 10 & gtc$MinDiff <= 20,]$arrival_bucket <- '10-20 min late'

gtc[gtc$MinDiff > 5 & gtc$MinDiff <= 10,]$arrival_bucket <- '6-10 min late'

gtc[gtc$MinDiff > 3 & gtc$MinDiff <= 5,]$arrival_bucket <- '4-5 min late'

gtc[gtc$MinDiff >= 1 & gtc$MinDiff <= 3,]$arrival_bucket <- '1-3 min late'

gtc[gtc$MinDiff == 0,]$arrival_bucket <- 'On time'

gtc[gtc$MinDiff <= (-1) & gtc$MinDiff >= (-3),]$arrival_bucket <- '1-3 min early'

gtc[gtc$MinDiff < (-3) & gtc$MinDiff >= (-5),]$arrival_bucket <- '4-5 min early'

gtc[gtc$MinDiff < (-5) & gtc$MinDiff >= (-10),]$arrival_bucket <- '6-10 min early'

gtc[gtc$MinDiff < (-10) & gtc$MinDiff >= (-20),]$arrival_bucket <- '10-20 min early'

gtc[gtc$MinDiff < (-20) ,]$arrival_bucket <- '20+ min early'


dayshift <- gtc[gtc$shift == 'DayShift',]
nightshift <- gtc[gtc$shift == 'NightShift',]


# calculate performance ontime
performance_ontime<-gtc[gtc$arrival_bucket == '20+ min early'
              |  gtc$arrival_bucket == '10-20 min early'
              |  gtc$arrival_bucket == '6-10 min early'
              |  gtc$arrival_bucket == '4-5 min early'
              |  gtc$arrival_bucket == '1-3 min early'
              |  gtc$arrival_bucket == 'On time',]


# calculate total jobs per date and hour
df_per_date <- group_by(gtc, Date) %>%
  summarise(JobTotal = sum(Count))

df_performance_ontime <- group_by(performance_ontime, Date) %>%
  summarise(JobSum = sum(Count))
df_performance_ontime <- merge(df_performance_ontime, df_per_date, by = c('Date') )
df_performance_ontime$Percent <- round((df_performance_ontime$JobSum / df_performance_ontime$JobTotal)*100,2)



```


```{r echo= FALSE,fig.width=18, fig.height=10,warning=FALSE, message= FALSE}
### Day shift. Jobs on time in %%  

# calculate performance ontime
performance_ontime<-dayshift[dayshift$arrival_bucket == '20+ min early'
              |  dayshift$arrival_bucket == '10-20 min early'
              |  dayshift$arrival_bucket == '6-10 min early'
              |  dayshift$arrival_bucket == '4-5 min early'
              |  dayshift$arrival_bucket == '1-3 min early'
              |  dayshift$arrival_bucket == 'On time',]


# calculate total jobs per date and hour
df_per_date <- group_by(dayshift, Date) %>%
  summarise(JobTotal = sum(Count))

df_performance_DS_ontime <- group_by(performance_ontime, Date) %>%
  summarise(JobSum = sum(Count))
df_performance_DS_ontime <- merge(df_performance_DS_ontime, df_per_date, by = c('Date'))
df_performance_DS_ontime$Percent <- round((df_performance_DS_ontime$JobSum / df_performance_DS_ontime$JobTotal)*100,2)


```



```{r echo= FALSE,fig.width=18, fig.height=10,warning=FALSE, message= FALSE}
### Night shift. Jobs on time in %%  
# calculate performance ontime
performance_ontime<-nightshift[nightshift$arrival_bucket == '20+ min early'
              |  nightshift$arrival_bucket == '10-20 min early'
              |  nightshift$arrival_bucket == '6-10 min early'
              |  nightshift$arrival_bucket == '4-5 min early'
              |  nightshift$arrival_bucket == '1-3 min early'
              |  nightshift$arrival_bucket == 'On time',]


# calculate total jobs per date and hour
df_per_date <- group_by(nightshift, Date) %>%
  summarise(JobTotal = sum(Count))

df_performance_NS_ontime <- group_by(performance_ontime, Date) %>%
  summarise(JobSum = sum(Count))
df_performance_NS_ontime <- merge(df_performance_NS_ontime, df_per_date, by = c('Date') )
df_performance_NS_ontime$Percent <- round((df_performance_NS_ontime$JobSum / df_performance_NS_ontime$JobTotal)*100,2)


```


```{r echo= FALSE,fig.width=18, fig.height=10,warning=FALSE, message= FALSE}
### Yesterday jobs up to 3 min late in %% 
## 3 min late

# calculate performance ontime
performance_3min<-gtc[gtc$arrival_bucket == '20+ min early'
              |  gtc$arrival_bucket == '10-20 min early'
              |  gtc$arrival_bucket == '6-10 min early'
              |  gtc$arrival_bucket == '4-5 min early'
              |  gtc$arrival_bucket == '1-3 min early'
              |  gtc$arrival_bucket == 'On time'
              |  gtc$arrival_bucket == '1-3 min late',]



# calculate total jobs per date and hour
df_per_date <- group_by(gtc, Date) %>%
  summarise(JobTotal = sum(Count))

df_performance_3min <- group_by(performance_3min, Date) %>%
  summarise(JobSum = sum(Count))
df_performance_3min <- merge(df_performance_3min, df_per_date, by = c('Date') )
df_performance_3min$Percent <- round((df_performance_3min$JobSum / df_performance_3min$JobTotal)*100,2)


```



```{r echo= FALSE,fig.width=18, fig.height=10,warning=FALSE, message= FALSE}
### Day shift. Jobs up to 3 min late in %% 
## 3 min late

# calculate performance ontime
performance_3min<-dayshift[dayshift$arrival_bucket == '20+ min early'
              |  dayshift$arrival_bucket == '10-20 min early'
              |  dayshift$arrival_bucket == '6-10 min early'
              |  dayshift$arrival_bucket == '4-5 min early'
              |  dayshift$arrival_bucket == '1-3 min early'
              |  dayshift$arrival_bucket == 'On time'
              |  dayshift$arrival_bucket == '1-3 min late',]



# calculate total jobs per date and hour
df_per_date <- group_by(dayshift, Date) %>%
  summarise(JobTotal = sum(Count))

df_performance_DS_3min <- group_by(performance_3min, Date) %>%
  summarise(JobSum = sum(Count))
df_performance_DS_3min <- merge(df_performance_DS_3min, df_per_date, by = c('Date') )
df_performance_DS_3min$Percent <- round((df_performance_DS_3min$JobSum / df_performance_DS_3min$JobTotal)*100,2)

```



```{r echo= FALSE,fig.width=18, fig.height=10,warning=FALSE, message= FALSE}
### Night shift. Jobs up to 3 min late in %% 
## 3 min late

# calculate performance ontime
performance_3min<-nightshift[nightshift$arrival_bucket == '20+ min early'
              |  nightshift$arrival_bucket == '10-20 min early'
              |  nightshift$arrival_bucket == '6-10 min early'
              |  nightshift$arrival_bucket == '4-5 min early'
              |  nightshift$arrival_bucket == '1-3 min early'
              |  nightshift$arrival_bucket == 'On time'
              |  nightshift$arrival_bucket == '1-3 min late',]



# calculate total jobs per date and hour
df_per_date <- group_by(nightshift, Date) %>%
  summarise(JobTotal = sum(Count))

df_performance_NS_3min <- group_by(performance_3min, Date) %>%
  summarise(JobSum = sum(Count))
df_performance_NS_3min <- merge(df_performance_NS_3min, df_per_date, by = c('Date') )
df_performance_NS_3min$Percent <- round((df_performance_NS_3min$JobSum / df_performance_NS_3min$JobTotal)*100,2)


```


##Daily performance statistics
```{r echo= FALSE,fig.width=18, fig.height=10,warning=FALSE, message= FALSE}
day<-c(ds,df_performance_DS_3min$Percent,df_performance_DS_ontime$Percent)
night<-c(ns,df_performance_NS_3min$Percent,df_performance_NS_ontime$Percent)
total<-c(nrow(gtc2),df_performance_3min$Percent,df_performance_ontime$Percent)

tbl<-rbind(day,night,total)
#colnames(tbl, do.NULL = TRUE, prefix = "")
colnames(tbl) <- c("Jobs", "On Time+3mins %","On Time %")
tbl
```

## Jobs and drivers chart

```{r echo= FALSE,fig.width=18, fig.height=10,warning=FALSE, message= FALSE}
#doing the necesary work
names(drivers) <- c('ID','Timestamp','VehicleType','OnlineDrivers')
drivers$Service <- ''
drivers$Service[drivers$VehicleType == 'Driver Direct'] <- 'Lite'
drivers$Service[drivers$VehicleType != 'Driver Direct'] <- 'GTC'

drivers$Timestamp <- as.POSIXct(drivers$Timestamp)

 # sum by GTC and GTLite for each 3 min
drivers_sum <- group_by(drivers, Service, Timestamp)
drivers_sum <- summarise(drivers_sum, sum_drivers = sum(OnlineDrivers))

# keep date and only HOUR for grouping
drivers_sum$Timestamp <- as.POSIXct(strptime(drivers_sum$Timestamp, "%Y-%m-%d %H"))

drivers_per_hour <- group_by(drivers_sum, Timestamp, Service)
drivers_per_hour <- summarise(drivers_per_hour, driver=round(mean(sum_drivers)))


GTC <- drivers_per_hour[drivers_per_hour$Service == 'GTC',]
Lite <- drivers_per_hour[drivers_per_hour$Service == 'Lite',]

names(GTC)[3] <- 'GTC_drivers'
names(Lite)[3] <- 'Lite_drivers'

DRIVERS <- subset(merge(GTC, Lite, by = 'Timestamp', all = TRUE), select = c(Timestamp, GTC_drivers, Lite_drivers))

DRIVERS$Hour <- seq(0,23,1)

write.xlsx(DRIVERS, file=filename, sheetName="Drivers") 


library(reshape2)
DRIVERS <- melt(DRIVERS[c('Hour','GTC_drivers', 'Lite_drivers')], id = 'Hour')

library(plyr)

# calculate midpoints of bars (simplified using comment by @DWin)
DRIVERS <- ddply(DRIVERS, .(Hour), 
   transform, pos = cumsum(value) - (0.5 * value)
)    

detach("package:dplyr", unload = T)
library(dplyr)


#GTC Jobs working (but not the chart)
file <- jobhistory
yesterday <- as.Date(Sys.time()-(60*60*24))
    

file <- file[grepl(yesterday, file$TimeAccepted) |  grepl(yesterday, file$TimeArrived) | grepl(yesterday, file$TimePoB) | grepl(yesterday, file$TimeCompleted),]

    
# calculate time for each stage
file['OnRouteToPickUp,min'] <- round(difftime(file$TimeArrived, file$TimeAccepted, units = "mins"),1)
file['WaitingForPassenger,min'] <- round(difftime(file$TimePoB, file$TimeArrived, units = "mins"),1)
file['Pob,min'] <- round(difftime(file$TimeCompleted, file$TimePoB, units = "mins"),1)

# order by UserName, TimeAccepted to calulate 'Free' time for drivers between journeys
library(plyr)
ordered <- arrange(file, UserName, TimeArrived)
ordered['Weekday'] <- weekdays(as.Date(ordered$jobDate))
ordered$Weekday <- factor(ordered$Weekday,levels=c('Monday', 'Tuesday', 'Wednesday', 'Thursday', 'Friday', 'Saturday', 'Sunday'))

# create new column with class 'difftime' for calculation of Free driver time
ordered['Free,min'] <- ordered$`Pob,min`

with_free_time <- data.frame()

for (driver in unique(ordered$UserName) ) {
     onedriver <- ordered[ordered$UserName == driver,]
     for (i in 1:(length(onedriver$id)-1) ) {
       onedriver['Free,min'][1,] <- 0
       onedriver['Free,min'][i,] <- round(difftime(onedriver$TimeAccepted[i+1], onedriver$TimeCompleted[i], units = "mins"),1)
       onedriver['Free,min'][length(onedriver$id),] <- 0
       } 
with_free_time <- rbind(with_free_time, onedriver)
    }

#write back data clean from waiting time <= 0 and > 2 hours

ordered <- with_free_time[with_free_time$`Free,min` > 0 & with_free_time$`Free,min` < 120,]


# subset necessary data
pickup <- subset(ordered, select = c(id, UserName, TimeAccepted,`OnRouteToPickUp,min`, Weekday))
waiting <- subset(ordered, select = c(id, UserName, TimeArrived,`WaitingForPassenger,min`, Weekday))
pob <- subset(ordered, select = c(id, UserName, TimePoB,`Pob,min`, Weekday))
free <- subset(ordered, select = c(id, UserName, TimeCompleted,`Free,min`, Weekday))

# add Hour column for each type of event
pickup['Hour'] <- as.numeric(format(pickup$TimeAccepted, "%H"))
waiting['Hour'] <- as.numeric(format(waiting$TimeArrived, "%H"))
pob['Hour'] <- as.numeric(format(pob$TimePoB, "%H"))
free['Hour'] <- as.numeric(format(free$TimeCompleted, "%H"))

# add status column for plotting all the statuses in one plot
pickup['Status'] <- 'PICK UP'
waiting['Status'] <- 'WAITING FOR PASSENGER'
pob['Status'] <- 'POB'
free['Status'] <- 'FREE'


# mean PICK UP
mean_pickup <- group_by(pickup, Hour, Status) %>%
  summarise(`mean_PickUp,min` = mean(`OnRouteToPickUp,min`) )
names(mean_pickup) <- c('Hour', 'Status', 'mean')
# mean WAITING
mean_waiting <- group_by(waiting, Hour, Status) %>%
  summarise(`mean_WaitingForPassenger,min` = mean(`WaitingForPassenger,min`))
names(mean_waiting) <- c('Hour', 'Status', 'mean')

# mean POB
mean_pob <- group_by(pob, Hour, Status) %>%
  summarise(`mean_Pob,min` = mean(`Pob,min`) )
names(mean_pob) <- c('Hour', 'Status', 'mean')

# mean Free
mean_free <- group_by(free, Hour,  Status) %>%
  summarise(`mean_Free,min` = mean(`Free,min`) )
names(mean_free) <- c('Hour',  'Status', 'mean')

# merge all statuses in one
means <- rbind(mean_pickup, mean_waiting, mean_pob, mean_free)

means$mean <- round( as.numeric(means$mean),0)

means$Status <- factor(means$Status,levels=c('FREE', 'POB', 'WAITING FOR PASSENGER', 'PICK UP'))


library(plyr)

# calculate midpoints of bars (simplified using comment by @DWin)
means <- ddply(means, .(Hour), 
   transform, pos = cumsum(mean) - (0.5 * mean)
)    

detach("package:dplyr", unload = T)
library(dplyr)

#Anto search term
gtc_per_hour <- group_by(gtc, Hour, Type2) %>% summarise(total = sum(Count))

DRIVERS_ALL<-group_by(DRIVERS,Hour) %>% summarise(Drivers=sum(value))

DRIVERS_ALL$Hour<-DRIVERS_ALL$Hour+1
#gtc_per_hour_drivers<-c(gtc_per_hour,)

 ggplot(gtc_per_hour) +
    geom_bar(aes(x = Hour , y = total, fill = Type2 ),position = 'stack',stat="identity")  +
    ggtitle('Job Volume by Type and Online Drivers') +
    xlab('Hour') +
    ylab('Number of jobs(bars)/drivers(line)') +
    theme(text = element_text(size=16)) +
   geom_line(data=DRIVERS_ALL,aes(x=Hour,y=Drivers),color ='green',size=1.5) 
   
 
```


# Drivers worked yesterday

```{r echo= FALSE,fig.width=18, fig.height=10,warning=FALSE, message= FALSE}





    ggplot(DRIVERS, aes(x = Hour, y = value, fill = variable )) +
    geom_bar(position = 'stack',stat="identity")  +
    ggtitle('Drivers per hour') +
    xlab('Hour') +
    ylab('Driver Count') +
    theme(text = element_text(size=16)) +
    scale_x_continuous(breaks = seq(0,23,1), limit = c(-1,24)) +
    scale_fill_brewer(palette="Set1") +
    geom_text(aes(label = value, y = pos), size = 3)
  

```

#GTC JOBS  

###Journey time analysis (excluding DD drivers)

```{r echo= FALSE,fig.width=18, fig.height=10,warning=FALSE, message= FALSE}


# by hour for each status
    ggplot(means, aes(x = Hour, y = mean, fill = Status)) +
    geom_bar(stat = 'identity', position = 'stack') +
    scale_x_discrete(limit = seq(0,23,1), breaks = seq(0,23,1))+
    ggtitle('Mean journey duration') +
    ylab('Time in min') +
    geom_text(aes(label = mean, y = pos), size = 3) +
    theme(text = element_text(size=16))

  

write.xlsx(means, file=filename, sheetName="JourneyTime", append = T) 

```




### Data is cleaned from:

* 2200 - Red Bee National
* 6443 - BT Sports - Transport Captain
* G1, G2, G3, G4, G5, G6, G7, G8, G9.1, G9.5, GTC888, G50, G51, G5555, 7002
* LONGTC1387 (training jobs)


```{r echo= FALSE,fig.width=18, fig.height=10,warning=FALSE, message= FALSE}

# remove 
#2200 - Red Bee National
#6443 - BT Sports - Transport Captain
#G1, G2, G3, G4, G5, G6, G7, G8, G9.1, G9.5, GTC888, G50, G51, G5555, 7002
#LONGTC1387 (training jobs)

```

## Total number of bookings:  

```{r echo=FALSE, message=FALSE,warning=FALSE}
#store clened data to use later in performance
gtc_cleaned <- gtc
#bind back not cleaned data for job volume purpuses
gtc <- gtc2
nrow(gtc)

```

### including flipped trips:  

```{r echo=FALSE, message=FALSE,warning=FALSE}
nrow(gtc[substr(gtc$Driver,1,2) == 'DD' & !is.na(gtc$Driver),])
```



## Job Volume by Type

```{r echo= FALSE,fig.width=18, fig.height=10,warning=FALSE, message= FALSE}

gtc_per_hour <- group_by(gtc, Hour, Type2) %>% summarise(total = sum(Count))


 ggplot(gtc_per_hour, aes(x = Hour , y = total, fill = Type2 )) +
    geom_bar(position = 'stack',stat="identity")  +
    ggtitle('Job Volume by Type') +
    xlab('Hour') +
    ylab('Number of jobs') +
    theme(text = element_text(size=16))

write.xlsx(gtc_per_hour, file=filename, sheetName="VolumeByType", append = T) 
```


## Job Volume by Vehicle Type

```{r echo= FALSE,fig.width=18, fig.height=10,warning=FALSE, message= FALSE}

gtc_per_vehicle <- group_by(gtc, Hour, VehicleType) %>% summarise(total = sum(Count))


 ggplot(gtc_per_vehicle, aes(x = Hour , y = total, fill = VehicleType )) +
    geom_bar(position = 'stack',stat="identity")  +
    ggtitle('Job Volume by Vehicle Type') +
    xlab('Hour') +
    ylab('Number of jobs') +
    theme(text = element_text(size=16)) +
    scale_fill_brewer(palette="Paired")
 
write.xlsx(gtc_per_vehicle, file=filename, sheetName="VolumeByVehicle", append = T) 
```





## Performance


### Data is cleaned from irrelevant accounts plus:

* 'PickUpArea': All airport pickups (TW6, RH6, CM24, E16, LU2); 
* Integrated Platform jobs - One Transport and Morgan Stanley (Oscar). 



```{r echo= FALSE,fig.width=18, fig.height=10,warning=FALSE, message= FALSE}
## clean data from :
#All airport jobs (collecting from Heathrow, Gatwick, Luton, City and Stansted) #have been excluded e.g. PickUpArea = TW6, RH6, CM24, E16, LU2

#All One T Jobs (specifically because their ASAP jobs are automatically late from #the point at which they are injected into our dispatch queue) have been excluded #e.g. Job creation type = One Transport

#Remove Morgan Stanley (same logic applied to One Transport) e.g. Acc No = C6000 or #Acc Name = Morgan Stanley


gtc <- gtc_cleaned


```


### Performance (on time / 3 min late)

```{r echo= FALSE,fig.width=18, fig.height=10,warning=FALSE, message= FALSE}

#### MORE DETAILED ARRIVALS
gtc$arrival_bucket <- '0'

gtc[gtc$MinDiff > 20 ,]$arrival_bucket <- '20+ min late'

gtc[gtc$MinDiff > 10 & gtc$MinDiff <= 20,]$arrival_bucket <- '10-20 min late'

gtc[gtc$MinDiff > 5 & gtc$MinDiff <= 10,]$arrival_bucket <- '6-10 min late'

gtc[gtc$MinDiff > 3 & gtc$MinDiff <= 5,]$arrival_bucket <- '4-5 min late'

gtc[gtc$MinDiff >= 1 & gtc$MinDiff <= 3,]$arrival_bucket <- '1-3 min late'

gtc[gtc$MinDiff == 0,]$arrival_bucket <- 'On time'

gtc[gtc$MinDiff <= (-1) & gtc$MinDiff >= (-3),]$arrival_bucket <- '1-3 min early'

gtc[gtc$MinDiff < (-3) & gtc$MinDiff >= (-5),]$arrival_bucket <- '4-5 min early'

gtc[gtc$MinDiff < (-5) & gtc$MinDiff >= (-10),]$arrival_bucket <- '6-10 min early'

gtc[gtc$MinDiff < (-10) & gtc$MinDiff >= (-20),]$arrival_bucket <- '10-20 min early'

gtc[gtc$MinDiff < (-20) ,]$arrival_bucket <- '20+ min early'






###PERFORMACE
 # ON TIME

#'4-5 min early', '1-3 min early','On time', '1-3 min late', '4-5 min late', '6-10 min late', '10-20 min late', '20+ min late'


# calculate performance ontime
performance_ontime<-gtc[gtc$arrival_bucket == '20+ min early'
              |  gtc$arrival_bucket == '10-20 min early'
              |  gtc$arrival_bucket == '6-10 min early'
              |  gtc$arrival_bucket == '4-5 min early'
              |  gtc$arrival_bucket == '1-3 min early'
              |  gtc$arrival_bucket == 'On time',]



# calculate total jobs per date and hour
df_per_date <- group_by(gtc, Date, Hour, Type) %>%
  summarise(JobTotal = sum(Count))

df_performance_ontime <- group_by(performance_ontime, Date, Weekday, Hour, Type) %>%
  summarise(JobSum = sum(Count))
df_performance_ontime <- merge(df_performance_ontime, df_per_date, by = c('Date','Hour','Type') )
df_performance_ontime$Percent <- round((df_performance_ontime$JobSum / df_performance_ontime$JobTotal)*100,2)




df_performance_ontime$Percent_bucket <- cut(
  df_performance_ontime$Percent, breaks = c(0,75,95,100)
)



    ggplot(df_performance_ontime, aes(x = Hour, y = Percent, fill = Percent_bucket)) +
    geom_bar(position = 'stack', stat='identity') +
    facet_wrap(~Type) +
    ggtitle('Performance (arrival on time)') +
    theme(text = element_text(size=16)) +
    geom_text(aes(label = Percent), size = 4)




```




```{r echo= FALSE,fig.width=18, fig.height=10,warning=FALSE, message= FALSE}
## 3 min late

# '1-3 min early','On time', '1-3 min late', '4-5 min late', '6-10 min late', '10-20 min late', '20+ min late'


# calculate performance ontime
performance_3min<-gtc[gtc$arrival_bucket == '20+ min early'
              |  gtc$arrival_bucket == '10-20 min early'
              |  gtc$arrival_bucket == '6-10 min early'
              |  gtc$arrival_bucket == '4-5 min early'
              |  gtc$arrival_bucket == '1-3 min early'
              |  gtc$arrival_bucket == 'On time'
              |  gtc$arrival_bucket == '1-3 min late',]



# calculate total jobs per date and hour
df_per_date <- group_by(gtc, Date, Hour, Type) %>%
  summarise(JobTotal = sum(Count))

df_performance_3min <- group_by(performance_3min, Date, Weekday, Hour, Type) %>%
  summarise(JobSum = sum(Count))
df_performance_3min <- merge(df_performance_3min, df_per_date, by = c('Date','Hour', 'Type') )
df_performance_3min$Percent <- round((df_performance_3min$JobSum / df_performance_3min$JobTotal)*100,2)




df_performance_3min$Percent_bucket <- cut(
  df_performance_3min$Percent, breaks = c(0,75,95,100)
)




ggplot(df_performance_3min, aes(x = Hour, y = Percent, fill = Percent_bucket)) +
    geom_bar(position = 'stack', stat='identity') +
    facet_wrap(~Type) +
    ggtitle('Performance (inc. arrival 3 min late)') +
    theme(text = element_text(size=16)) +
    geom_text(aes(label = Percent), size = 4)



```








```{r echo= FALSE,fig.width=18, fig.height=10,warning=FALSE, message= FALSE}


# make buckets for late and early arrivals

gtc$arrival_bucket <- '0'

gtc[gtc$MinDiff >= (-5) & gtc$MinDiff <= 5,]$arrival_bucket <- 'On time (-5,+5)'



gtc[gtc$MinDiff > 5 & gtc$MinDiff <= 10,]$arrival_bucket <- '6-10 min late'
gtc[gtc$MinDiff > 10 ,]$arrival_bucket <- '10+ min late'

gtc[gtc$MinDiff < (-5) & gtc$MinDiff >= (-10),]$arrival_bucket <- '6-10 min early'
gtc[gtc$MinDiff < (-10) ,]$arrival_bucket <- '10+ min early'


# calculate total jobs per date and hour
df_per_date <- group_by(gtc, Type) %>%
  summarise(JobTotal = sum(Count))

# calculate performance ontime
df_by_arrival <- group_by(gtc, arrival_bucket, Type) %>%
  summarise(JobSum = sum(Count))


df_by_arrival <- merge(df_by_arrival, df_per_date, by = c('Type') )
df_by_arrival$Percent <- round((df_by_arrival$JobSum / df_by_arrival$JobTotal)*100,2)


write.xlsx(df_by_arrival, file=filename, sheetName="Arrivals", append = TRUE)


df_by_arrival$arrival_bucket <- factor(as.character(df_by_arrival$arrival_bucket),levels= rev(c('10+ min early', '6-10 min early', 'On time (-5,+5)', '6-10 min late', '10+ min late')))
```






## Arrivals

```{r echo= FALSE,fig.width=18, fig.height=10,warning=FALSE, message= FALSE}
# plot for all arrival times
df_by_arrival <- df_by_arrival[rev(order(df_by_arrival$arrival_bucket)),] 

#p <- 
  ggplot(df_by_arrival, aes(x = Type , y = Percent, fill = arrival_bucket, group = arrival_bucket, order = -as.numeric(arrival_bucket))) +
    geom_bar(position = 'stack', stat='identity') +
    theme(text = element_text(size=20)) +
    scale_y_continuous(breaks = seq(0,100,10))+
  ggtitle('Arrivals in percents') +
  xlab('Date') +
  ylab('Percent of jobs')
#ggsave(filename="Arrivals in percents.jpg", plot=p,height = 7, width = 14)


```


```{r echo= FALSE,fig.width=18, fig.height=10,warning=FALSE, message= FALSE}
#### MORE DETAILED ARRIVALS


gtc[gtc$MinDiff > 20 ,]$arrival_bucket <- '20+ min late'

gtc[gtc$MinDiff > 10 & gtc$MinDiff <= 20,]$arrival_bucket <- '10-20 min late'

gtc[gtc$MinDiff > 5 & gtc$MinDiff <= 10,]$arrival_bucket <- '6-10 min late'

gtc[gtc$MinDiff > 3 & gtc$MinDiff <= 5,]$arrival_bucket <- '4-5 min late'

gtc[gtc$MinDiff >= 1 & gtc$MinDiff <= 3,]$arrival_bucket <- '1-3 min late'

gtc[gtc$MinDiff == 0,]$arrival_bucket <- 'On time'

gtc[gtc$MinDiff <= (-1) & gtc$MinDiff >= (-3),]$arrival_bucket <- '1-3 min early'

gtc[gtc$MinDiff < (-3) & gtc$MinDiff >= (-5),]$arrival_bucket <- '4-5 min early'

gtc[gtc$MinDiff < (-5) & gtc$MinDiff >= (-10),]$arrival_bucket <- '6-10 min early'

gtc[gtc$MinDiff < (-10) & gtc$MinDiff >= (-20),]$arrival_bucket <- '10-20 min early'

gtc[gtc$MinDiff < (-20) ,]$arrival_bucket <- '20+ min early'


# calculate total jobs per date and hour
df_per_date <- group_by(gtc, Type) %>%
  summarise(JobTotal = sum(Count))

# calculate performance ontime
df_by_arrival <- group_by(gtc, Type, arrival_bucket) %>%
  summarise(JobSum = sum(Count))


df_by_arrival <- merge(df_by_arrival, df_per_date, by = c('Type') )
df_by_arrival$Percent <- round((df_by_arrival$JobSum / df_by_arrival$JobTotal)*100,2)


write.xlsx(df_by_arrival, file=filename, sheetName="ArrivalsDetailed", append=TRUE)


df_by_arrival$arrival_bucket <- factor(df_by_arrival$arrival_bucket,levels= rev(c('20+ min early', '10-20 min early', '6-10 min early','4-5 min early', '1-3 min early','On time', '1-3 min late', '4-5 min late', '6-10 min late', '10-20 min late', '20+ min late')))


df_by_arrival <- df_by_arrival[rev(order(df_by_arrival$arrival_bucket)),] 


# plot for all arrival times
#p <- 
  ggplot(df_by_arrival, aes(x = Type , y = Percent, fill = arrival_bucket, group = arrival_bucket, order = -as.numeric(arrival_bucket))) +
    geom_bar(position = 'stack', stat='identity') +
    theme(text = element_text(size=20)) +
    scale_y_continuous(breaks = seq(0,100,10))+
    ggtitle('Arrivals in percents. Detailed') +
    xlab('Date') +
    ylab('Percent of jobs')
#ggsave(filename="Arrivals in percents.Detailed.jpg", plot=p,height = 7, width = 14)

```




```{r echo= FALSE,fig.width=18, fig.height=10,warning=FALSE, message= FALSE}

# calculate total jobs per date and ASAP
df_per_date <- group_by(gtc, Type2) %>%
  summarise(JobTotal = sum(Count))

# calculate performance ontime
df_by_arrival <- group_by(gtc, Type2, arrival_bucket) %>%
  summarise(JobSum = sum(Count))


df_by_arrival <- merge(df_by_arrival, df_per_date, by = c('Type2') )
df_by_arrival$Percent <- round((df_by_arrival$JobSum / df_by_arrival$JobTotal)*100,2)


write.xlsx(df_by_arrival, file=filename, sheetName="ArrivalsASAP_PREBOOK", append=TRUE)


df_by_arrival$arrival_bucket <- factor(df_by_arrival$arrival_bucket,levels= rev(c('20+ min early', '10-20 min early', '6-10 min early','4-5 min early', '1-3 min early','On time', '1-3 min late', '4-5 min late', '6-10 min late', '10-20 min late', '20+ min late')))

df_by_arrival <- df_by_arrival[rev(order(df_by_arrival$arrival_bucket)),] 

# plot for all arrival times

#p <- 
  ggplot(df_by_arrival, aes(x = Type2 , y = Percent, fill = arrival_bucket, group = arrival_bucket, order = -as.numeric(arrival_bucket))) +
    geom_bar(position = 'stack', stat='identity') +
    theme(text = element_text(size=20)) +
    scale_y_continuous(breaks = seq(0,100,10))+
  ggtitle('Arrivals in percents. ASAP and Prebook') +
  xlab('Date') +
  ylab('Percent of jobs')
#ggsave(filename="Arrivals in percents. ASAP and Prebook.jpg", plot=p,height = 7, width = 14)

```




```{r echo= FALSE,fig.width=20, fig.height=15,warning=FALSE, message= FALSE}
# calculate total jobs per date and grade
df_per_date <- group_by(gtc, Grade) %>%
  summarise(JobTotal = sum(Count))

# calculate performance ontime
df_by_arrival <- group_by(gtc, arrival_bucket, Grade) %>%
  summarise(JobSum = sum(Count))


df_by_arrival <- merge( df_per_date, df_by_arrival, by = c( 'Grade') , all = TRUE)
df_by_arrival$Percent <- round((df_by_arrival$JobSum / df_by_arrival$JobTotal)*100,2)


write.xlsx(df_by_arrival, file=filename, sheetName="ArrivalsGrade", append=TRUE)


df_by_arrival$arrival_bucket <- factor(df_by_arrival$arrival_bucket,levels= rev(c('20+ min early', '10-20 min early', '6-10 min early','4-5 min early', '1-3 min early','On time', '1-3 min late', '4-5 min late', '6-10 min late', '10-20 min late', '20+ min late')))


df_by_arrival<-df_by_arrival[df_by_arrival$Grade != 'Test Grade',]

# plot for all arrival times

df_by_arrival <- df_by_arrival[rev(order(df_by_arrival$arrival_bucket)),] 


#p <- 
  ggplot(df_by_arrival, aes(x = Grade , y = Percent, fill = arrival_bucket, group = arrival_bucket, order = -as.numeric(arrival_bucket))) +
    geom_bar(position = 'stack', stat='identity') +
    theme(axis.text.x = element_text(angle = 50, hjust = 1),text = element_text(size=20)) +
    scale_y_continuous(breaks = seq(0,100,10))+
    ggtitle('Arrivals in percents by Grade') +
    xlab('Date') +
    ylab('Percent of jobs')
#ggsave(filename="Arrivals in percents by Grade.jpg", plot=p,height = 7, width = 14)
```










### Performance by Grade

```{r echo= FALSE,fig.width=18, fig.height=10,warning=FALSE, message= FALSE}
### performance per grade

# calculate total jobs per date and hour
df_per_date <- group_by(gtc, Date, Hour, Grade) %>%
  summarise(JobTotal = sum(Count))

df_performance_3min <- group_by(performance_3min, Date, Weekday, Hour, Grade) %>%
  summarise(JobSum = sum(Count))
df_performance_3min <- merge(df_performance_3min, df_per_date, by = c('Date','Hour','Grade') )
df_performance_3min$Percent <- round((df_performance_3min$JobSum / df_performance_3min$JobTotal)*100,2)




df_performance_3min$Percent_bucket <- cut(
  df_performance_3min$Percent, breaks = c(0,75,95,100)
)



ggplot(df_performance_3min, aes(x = Hour, y = Percent, fill = Percent_bucket)) +
    geom_bar(position = 'stack', stat='identity') +
    facet_wrap(~Grade) +
    ggtitle('Performance by Grade (inc. arrival 3 min late)') +
    theme(text = element_text(size=16))
```



### Performance asap / prebook



```{r echo= FALSE,fig.width=18, fig.height=10,warning=FALSE, message= FALSE}
# calculate total jobs per date and hour and asap
df_per_date <- group_by(gtc, Date, Hour, Type2) %>%
  summarise(JobTotal = sum(Count))

df_performance_3min <- group_by(performance_3min, Date, Weekday, Hour, Type2) %>%
  summarise(JobSum = sum(Count))
df_performance_3min <- merge(df_performance_3min, df_per_date, by = c('Date','Hour','Type2') )
df_performance_3min$Percent <- round((df_performance_3min$JobSum / df_performance_3min$JobTotal)*100,2)




df_performance_3min$Percent_bucket <- cut(
  df_performance_3min$Percent, breaks = c(0,75,95,100)
)



ggplot(df_performance_3min, aes(x = Hour, y = Percent, fill = Percent_bucket)) +
    geom_bar(position = 'stack', stat='identity') +
    facet_wrap(~Type2) +
    ggtitle('Performance by Type (inc. arrival 3 min late)') +
    theme(text = element_text(size=16))




```